RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-04 doc/paper.tex
Conclusions

\section{Conclusions and future work}\label{sec:conclusions}

>>>>

\section{Conclusions and future work}\label{sec:conclusions}
  This paper deals with solving the well--known Symbolic regression (SR)  problem. This problem is a generalization of more interdisciplinary appearing  linear and logistic regression problems. SR problem have been intensively studied in the literature over the last 15 years, where a few dozens of algorithms were constructed, mainly based on Genetic programming and on the application of different kinds of neural networks. We proposed a meta-heuristic approach, called \textsc{Rils}-\textsc{Rols}. It is based on the Iterative local search (ILS) scheme. The first crucial concept within this scheme is utilizing the oridinary least square method to efficiently determine coefficients in the candidate solutions. Another key aspect is the use of a carefully constructed fitness function, which is a combination of three important scores: RMSE, $R^2$  scores and the size of model (solution).  Last but not least, the neighbor of solution in the local search is carefully defined that suits to small modifications of a three that represents solutions (models). \textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from literature on the two ground truth benchmark sets from literature. Additionally, we introduced a non-biased benchmark set of randomly generated instances.  The experimental evaluation confirmed efficiently of out method which was able to produce the best average ranking in terms of exact percentage in comparison to all other competitors on all ground-truth instances, and in presence of three different levels of noise in the input data. In all cases, new best average-percentages are obtained in the literature by means of \textsc{Rils-Rols} method. In some cases, these differences are statistically significant in favor of our \textsc{Rils-Rols} method. Moreover, scalability and robustness of our method is  checked and confirmed on the randomly generated instances in terms of a few different criteria such as the size of model, the number of variables, average runtimes, etc.  \fxnote{TODO: case-study about large-scale data to be added}

  In the future work, one could think of  make a hybrid of \textsc{Rils-Rols} method with some other meta-heuristics, or replacing ILS scheme of \textsc{Rils-Rils} with, for example, Variable neighborhood search meta-heuristic. Additionally, as a proof of the concept, our tool will be provided to various research communities out of the are of Computer science, such as the ones from physics ot chemistry to seek for new hypotheses or o obtain insights on their experimental data.
